CLPFUDatabase: A suite of R packages for energy conversion chain analysis

### 2024-01-08 paper.Rmd
Minor changes.

Broadly speaking, 
four calculation steps are required to create a CL-PFU database. 
Each step is assisted by functions in one or more of the new `R` packages.
First, the IEA's primary- and final-stage 
EWEB data must be converted
to RUVY matrices for each country and year, 
a task accomplished by functions in the [IEATools][link-ieatools] package [@Heun-IEATools:2023]. 
Second, human and animal muscle work must be calculated from 
[International Labor Organization][link-ilo] (ILO) and
[Food and Agriculture Organization][link-fao] (FAO) data,
following the methodology of @Steenwyk:2022ww, 
using functions in the [MWTools][link-mwtools] package [@Marshall:2023ab]. 
The muscle work data must also be converted to RUVY matrices.
Third, the IEA's primary- and final-stage ECC data 
must be extended to the useful stage by
(a) allocating final stage energy to end-use machines and
(b) multiplying allocated final energy by the 
final-to-useful efficiency of each machine.
This task is accomplished by functions in the
[Recca][link-recca] [@Heun-Recca:2023]
package.
Fourth, ECCs must be converted from energy terms to exergy terms. 
This step is also performed by functions in the [Recca][link-recca] package.

The steps to create the PSUT matrices for each country and each year
are accomplished by a
[targets][link-targets] [@Landau:2021aa]
computation pipeline
available in the [PFUPipeline][link-pfupipeline]
package.
A unique feature of the
[PFUPipeline][link-pfupipeline]
enabled by the [Recca][link-recca] package 
is an innovative exemplar system that allows
analyses to proceed when allocation or efficiency data are unavailable for a country.
When allocations or efficiencies are missing,
a string of exemplar countries or regions
are queried for the required information.
For example, exemplars for Belgium are
France, Europe, and ultimately, the World, in that order.
The design of the calculation pipeline in the [PFUPipeline][link-pfupipeline] package 
allows allocation and efficiency data
for any country or year to be added at a later date 
to improve the database.

@@

The packages in the following table support creation of the CL-PFU database
are available on GitHub.

>>>>

Broadly speaking, 
four calculation steps are required to create a CL-PFU database. 
Each step is assisted by functions in one or more of the new `R` packages.
First, the IEA's primary- and final-stage 
EWEB data must be converted
to RUVY matrices for each country and year, 
a task accomplished by functions in the [IEATools][link-ieatools] package [@Heun-IEATools:2023]. 
Second, human and animal muscle work must be calculated from 
[International Labor Organization][link-ilo] (ILO) and
[Food and Agriculture Organization][link-fao] (FAO) data,
following the methodology of @Steenwyk:2022ww, 
using functions in the [MWTools][link-mwtools] package [@Marshall:2023ab]. 
The muscle work data must also be converted to RUVY matrices.
Third, the IEA's primary- and final-stage ECC data 
must be extended to the useful stage by
(a) allocating final stage energy to end-use machines and
(b) multiplying allocated final energy by the 
final-to-useful efficiency of each machine.
This task is accomplished by functions in the
[Recca][link-recca]
package [@Heun-Recca:2023].
Fourth, ECCs must be converted from energy terms to exergy terms. 
This step is also performed by functions in the [Recca][link-recca] package.

The steps to create the PSUT matrices for each country and each year
are accomplished by a
[targets][link-targets] [@Landau:2021aa]
computation pipeline
available in the [PFUPipeline][link-pfupipeline]
package [@Heun-PFUPipeline:2023].
A unique feature of the
[PFUPipeline][link-pfupipeline]
enabled by the [Recca][link-recca] package 
is an innovative exemplar system that allows
analyses to proceed when allocation or efficiency data are unavailable for a country.
When allocations or efficiencies are missing,
a string of exemplar countries or regions
are queried for the required information.
For example, exemplars for Belgium are
France, Europe, and ultimately, the World, in that order.
The design of the calculation pipeline in the [PFUPipeline][link-pfupipeline] package 
allows allocation and efficiency data
for any country or year to be added at a later date 
to improve the database.

@@

The packages in the following table support creation of the CL-PFU database and
are available on GitHub.
